What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-01-31 text/01_CogSci_abstract/paper.tex
motivation minor edits

A simple technique that seems to fit this bill is the \emph{binned histograms} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to on out of 15 bins that partition the range of plausible
values (established by a pre-test), such as 0--50\$, 50--100\$, \dots 700--750\$. Each
subject's slider ratings are normalized within each item, and the results are averaged across
subjects to obtain an estimate of the population's average belief about each item.

\ndg{should we also talk about the other dependent measures? i think part of what's interesting is comparing the different dependent measures to each other?}

\begin{itemize}
\item explain slider rating task
\item our goal here is to validate whether ``population-level beliefs'' are approximated well
  enough by normalized average slider ratings
\item use hierarchical Bayesian modeling
  \begin{itemize}
  \item calculate likelihoods from subjective beliefs
  \item each subjective belief is drawn from a population-level central tendency, which is a
    ``belief'' as well
  \end{itemize}
\end{itemize}

@@

\begin{table*}
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	Item & Bins (units, min, max, step) & Context sentence & GAN question & BH frame & PC frame \\
	\midrule
    coffee & degrees, $<$44, $>200$, 13& X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & his coffee was the following temperatures & The temperature of his coffee is N degrees.\\
	commute & minutes, 0, $>$98, 7 & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & she commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
	joke & children, 0, 14, 1  & X told a joke to 14 kids. & How many of the kids do you think laughed? & the following number of kids laughed & N of the children laughed.\\

>>>>

A simple technique that seems to fit this bill is the \emph{binned histograms} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to on out of 15 bins that partition the range of plausible
values (established by a pre-test), such as 0--50\$, 50--100\$, \dots 700--750\$. Each
subject's slider ratings are normalized within each item, and the results are averaged across
subjects to obtain an estimate of the population's average belief about each item. These
averaged normalized slider ratings per bin (henceforth: mean slider ratings) look intuitively
plausible and give good results if fed into cognitive models that predict behavior in language
or reasoning tasks, for instance.

Explanatory success notwithstanding, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of subjects'
individual beliefs? Are these measures consistent with subjects' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of ``what the crowd beliefs.''
Moreover, the model is able to capture subjects' behavior in all three task types reasonably
well, suggesting that what mean sliders measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

@@

\begin{table*}
  \footnotesize
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	Item & Bins (units, min, max, step) & Context sentence & GAN question & BH frame & PC frame \\
	\midrule
    coffee & degrees, $<$44, $>200$, 13& X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & his coffee was the following temperatures & The temperature of his coffee is N degrees.\\
	commute & minutes, 0, $>$98, 7 & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & she commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
	joke & children, 0, 14, 1  & X told a joke to 14 kids. & How many of the kids do you think laughed? & the following number of kids laughed & N of the children laughed.\\
